Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-14 article.rnw
Precompute the body-weight-based distance matrix in article.rnw.

<<include=FALSE>>=
	source("r/post-process.R")
	source("r/brute-post-process.R")
	source("r/mantel-test.R")
	source("r/coclassification-table.R")

@@

	#Precalculate the coclassification matrices, as these are active bindings and the slowest part of compilation.
	weighted_col_coclassification_matrix <- brute_data$weighted_col_coclassification_matrix
	weighted_row_coclassification_matrix <- brute_data$weighted_row_coclassification_matrix
@

>>>>

<<include=FALSE>>=
	source("r/post-process.R")
	source("r/brute-post-process.R")
	source("r/mantel-test.R")
	source("r/dist-matrix.R")
	source("r/coclassification-table.R")

@@

	#Precalculate the coclassification matrices, as these are active bindings and the slowest part of compilation.
	weighted_col_coclassification_matrix <- brute_data$weighted_col_coclassification_matrix
	weighted_row_coclassification_matrix <- brute_data$weighted_row_coclassification_matrix

	#Precalculate distances matrices as well.
	body_weight_distance_matrix <- build_dist_matrix(species_dat$name, species_dat$body_weight, function(w1,w2){abs(w1-w2)})
@
